ASR-Output-Correcting Webapp After 6 Years

### 2018-03-23 2018-tsd-brno/webapp.tex
interface desc

\noindent
\begin{tabularx}{\textwidth}{
    @{\hspace{1.5em}}% Space for left bullet
    >{\leavevmode\llap{\textbullet~}\raggedright}% Left bullet + formatting of column
    X% Left column specification
    @{\quad\hspace{1.5em}}% Space between columns + right bullet space
    >{\leavevmode\llap{\textbullet~}\raggedright\arraybackslash}% Right bullet + formatting of column
    X% Right column specification
    @{}% No column space on right
  }
  \em{common transcription applications} & \em{our application} \\
  are optimized for the case where there is no transcription available and it
  must be acquired from scratch &
    always assumes a transcription is available \\
  need no quality control: the user is free to enter whatever transcription she
  pleases and the ultimate measure is her satisfaction &
    needs the transcription to be accurate because it is used as training data
    for the acoustic model \\
  use alignment on the level of phrases, if any &
    uses alignment on the level of words \\
  are user-centric: the user transcribes whatever acoustic data they choose &
    is data-centric: the whole application with all its tools and persons
    revolves around the data set \\
  assumes the user wants to transcribe &
    assume the user want to listen and possibly read along and we want to
    animate her to submit transcriptions \\
  has no shared data between users &
    must count with collisions
\end{tabularx}

@@

>>>>

\noindent
\begin{tabularx}{\textwidth}{
    @{\hspace{1.5em}}% Space for left bullet
    >{\leavevmode\llap{\textbullet~}\raggedright}% Left bullet + formatting of column
    X% Left column specification
    @{\quad\hspace{1.5em}}% Space between columns + right bullet space
    >{\leavevmode\llap{\textbullet~}\raggedright\arraybackslash}% Right bullet + formatting of column
    X% Right column specification
    @{}% No column space on right
  }
  \em{common transcription applications} & \em{our application} \\
  are optimized for the case where there is no transcription available and it
  must be acquired from scratch &
    always assumes a transcription is available \\
  allow annotation of speakers &
    assumes all utterances come from the same speaker \\
  need no quality control: the user is free to enter whatever transcription she
  pleases and the ultimate measure is her satisfaction &
    needs the transcription to be accurate because it is used as training data
    for the acoustic model \\
  use alignment on the level of phrases, if any &
    uses alignment on the level of words \\
  are user-centric: the user transcribes whatever acoustic data they choose &
    is data-centric: the whole application with all its tools and persons
    revolves around the data set \\
  assumes the user wants to transcribe &
    assume the user want to listen and possibly read along and we want to
    animate her to submit transcriptions \\
  has no shared data between users &
    must count with collisions
\end{tabularx}

@@

\section{Description of the web application}

The application consists of several views:
\begin{enumerate}
\item{the start page where all recordings are listed and each points to a detail
view,}
\item{the detail view, where a recording can be played back, its transcription
is displayed and can be corrected by the user,}
\item{search page, where hits to a search query are listed and point to
corresponding positions in the recordings,}
\item{static pages with general information, contact etc.}
\end{enumerate}

We shall only discuss the detail view as the others are not relevant to this
article. Figure~\ref{fig:scn1lab} shows the interface during playback.
Figure~\ref{fig:scn2lab} shows the interface while a segment is being edited.
The interface in the figures is conveniently shown in English, although in
reality it is in Czech.

\begin{figure}[htpb]
\includegraphics[scale=0.6]{rc/radio-makon-en-1-lab.png}
\caption{Web interface during playback}
\label{fig:scn1lab}
\end{figure}

Legend to Figure~\ref{fig:scn1lab}:
\begin{enumerate}
\item{
    Header with
    \begin{itemize}
    \item{app name linking to start page,}
    \item{about link,}
    \item{search field and}
    \item{username input field;}
    \end{itemize}
}
\item{Identifier of the recording;}
\item{Automatically transcribed segments in gray;}
\item{Manually transcribed segments in black;}
\item{Currently played-back word highlighted by yellow background;}
\item{Marked word highlighted in regent st. blue;}
\item{
    Marked word info:
    \begin{itemize}
    \item{
        occurrence: the word with contextual capitalization and
        punctuation as it appeard in the text, currently being edited as the
        selected initial letter reveals,
    }
    \item{form: normalized word form as it appears in the word list,}
    \item{pronunciation: Czech phonetic transcription of the word,}
    \item{
        position: time of the beginning of the word in seconds from the
        start of the recording;
    }
    \end{itemize}
}
\item{
    Tools for storing:
    \begin{itemize}
    \item{direct links to the audio files,}
    \item{selecting the whole transcription for easy pasting,}
    \item{storing the decoded recording in the browser's IndexedDB;}
    \end{itemize}
}
\item{Graphical equalizer for compensating narrow-band noise;}
\item{
    Audio playback controls:
    \begin{itemize}
    \item{play/pause button,}
    \item{current playback position,}
    \item{playback scrollbar,}
    \item{total recording length;}
    \end{itemize}
}
\item{Current position reflected in URL fragment.}
\end{enumerate}

\begin{figure}[htpb]
\includegraphics[scale=0.6]{rc/radio-makon-en-2-lab.png}
\caption{Interface in the state of editing a segment, with labels}
\label{fig:scn2lab}
\end{figure}

Legend to Figure~\ref{fig:scn2lab}:
\begin{enumerate}
\item{
    Selecting a text range with the mouse defines the segment the user is about
    to transcribe;
}
\item{
    The edit tool with
    \begin{itemize}
    \item{textarea prefilled with the current transcription,}
    \item{playback button that plays the corresponding segment,}
    \item{save button and}
    \item{download-segment button, which initiates a file-save action for the
    corresponding segment.}
    \end{itemize}
}
\end{enumerate}

\subsection{Displaying the transcription}

Most transcribing programs show the transcription as a vertical list of
utterances, see Figure~\ref{fig:transcriber1} for an example of
{\em{Transcriber}}\footnote{trans.sourceforge.net}, a veteran open-source
transcription tool. We attribute this to the fact that the atomic elements of
the transcription are the user-entered utterances and their boundaries are
reliable. In our case, the atomic elements are words. There are sentences, sure,
but the segmentation to sentences by the ASR is very unreliable, so we want it
to be natural to transcribe a segment overlapping sentence boundaries.

This is one of the reasons why we display the transcription basically as a
single wrapped line.

The transcription display was designed to have these features:
\begin{itemize}
\item{Currently played-back word should be highlighted;}
\item{
    Manually transcribed segments should be clearly distinct from automatically
    transcribed ones;
    \label{feats:item:manualdistinct}
}
\item{
    Selecting one or more words with the mouse should trigger transcription mode
    for the selected text;
    upon a successful save, this should be merged into the display;
}
\item{
    Clicking a word should bring up its context info (we call this the
    \em{marked word} as the term \em{selected word} is already taken);
}
\item{
    The whole transcription should be shown at once for easy searching;
    \label{feats:item:showall}
}
\item{
    The page should be responsive;\label{feats:item:speed}
}
\end{itemize}

These requirements are harder to combine than it may seem. Notably
responsiveness is hard to combine with all of the other ones. Why is that so?

\begin{figure}[htpb]
\includegraphics[scale=0.4]{rc/transcriber1.png}
\caption{A screenshot of Transcriber}
\label{fig:transcriber1}
\end{figure}
